Multi-view 3D Aerosol Distribution Recovery

### 2013-07-31 article.tex
bookmark

%
% Some new commands I use in this text
%
% Note:
% Nice curly font is {\bm{\mathcal{D}}}
%
\newcommand{\OpSphere}{\mathbfcal{S}}
\newcommand{\OpRot}{\mathbfcal{R}}
%\newcommand{\OpDistance}{\mathbfcal{D}}
\newcommand{\OpDistance}{\bm{D}}
\newcommand{\OpCumsum}{\mathbfcal{C}}
\newcommand{\OpInt}{\mathbfcal{I}}
\newcommand{\OpCamera}{\mathbfcal{P}}
\newcommand{\Mask}{\mathbfcal{M}}
\newcommand{\Laplacian}{\mathbfcal{L}}
%\newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
\newcommand{\OpDiag}[1]{\mathbb{D}\left\{#1\right\}}
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\abbrev}[1]{\rm{#1}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}
\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images

\newcommand\authnote[1]{\textsuperscript{\normalfont#1}}
\newcommand\affilnote[1]{\textsuperscript{\normalfont#1}}
\providecommand\textsuperscript[1]{$^{#1}$}

@@

Any voxel generally contains both air molecules and aerosols.  We
focus on situations where there is only a single type of aerosol over
a scene. Hence, the three-element vector $[{\sigma}^{\rm
  aerosol},\varpi^{\rm aerosol},g]$ is uniform across the scene, but
the density distribution ${\bm n}$ is variable. As a numerical
approximation, assume that within any voxel, the molecular parameters
$\{ \beta^{\rm air}(k),\alpha^{\rm air}(k)\}$ and the aerosol density
$n(k)$ are constants, e.g., corresponding to the value at each voxel
center.  Following \cref{eq:tau}, the optical depth between the TOA
and voxel $k$ is
\begin{equation}
  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
  \label{eq:lSRn}
\end{equation}
We can write \cref{eq:lSRn} using matrix notation, $\vect{\tau}_{\rm
  SR}=\OpDistance^{\mathrm{Sun \rightarrow voxel}} \vect{\beta}$,
where $\vect{\tau}_{\rm SR}$ and $\vect{\beta}$ are column stack
vector representations of $\tau_{\rm SR}(k)$ and $\beta(q)$,
respectively. Similarly, the optical depth along a LOS to voxel $k$ is
expressed by element $k$ of $\vect{\tau}_{{\rm LOS}_c} =
\OpDistance^{\mathrm{voxel \rightarrow cam}} \vect{\beta}$ Here
$\vect{\tau}_{{\rm LOS}_c}$ is a column stack vector representation of
$\tau_{{\rm LOS}_c}(k)$.  The SR and LOS paths joining at each voxel
can form a single path from the TOA to camera $c$, yielding
\begin{equation}
  {\bm D}_c=
  {\bm D}^{\mathrm{Sun \rightarrow voxel}}+
  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
  \quad\text{ and }\quad
  \vect{\tau}_c=
  \vect{\tau}_{\rm SR}+
  \vect{\tau}_{{\rm LOS}_c}
  \;\;.
  \label{eq:D_tau_total}
\end{equation}

@@

In this paper, we assume that the type of the aerosol above an area is
known~\cite{Martonchik2009}. Hence, we focus on estimating the density
distribution ${\bm n}$.
% Most generally, this is the set $\left\{{\bm
%   n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
%     g}_{\lambda}\right\}_{\lambda}\right\}$ where some of the
% parameters depend on the spectral channel $\lambda$.  Usually, a
% single aerosol type dominates a scene. Furthermore, we assume that
% the type of the aerosol above an area is
% known~\cite{Martonchik2009}. Hence, we focus on estimating the
% density distribution ${\bm n}$.
At hand, we have $N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
  measured}_c\}_{c=1}^{N_{\rm views}}$. The recovery task is phrased
as optimization of an objective function that fits the image-formation
model to the measured photographs:
\begin{equation}
  \label{eq:minobjectiveA}
  \hat{\bm n} =
  \argmin_{{\bm n}} F({\bm n})
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  F({\bm n})
  = \sum_{c=1}^{N_{\rm views}}
  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2
  + \eta \Psi({\bm n})
\end{equation}
where $\Mask$ is a map that masks the areas around the sun, which are
overwhelmingly bright. %and the horizon.
% These regions are prone to dominant multiple scattering.
In Eq.~(\ref{eq:objectiveA}), $\Psi({\bm n})$ is a regularization term
that expresses some prior knowledge on the distribution, while $\eta$
is a regularization weight.  Since aerosol distributions are usually
fuzzy, it can be beneficial that regularization be a {\em smoothness
  term}, which penalizes energy in second order spatial derivatives
(3D Laplacian). Hence, we use
\begin{equation}
  \label{eq:regularizer}
  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2 = \| \Laplacian{\bm n}\|^2_2
\end{equation}
where $\Laplacian$ is a matrix representation of the 3D
\emph{Laplacian} operator.

>>>>

%
% Some new commands I use in this text
%
% Note:
% Nice curly font is {\bm{\mathcal{D}}}
%
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\abbrev}[1]{\rm{#1}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}
\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images

%
% Used symbols (only partial for now...)
%
\newcommand{\OpSphere}{\mathbfcal{S}}
\newcommand{\OpRot}{\mathbfcal{R}}
\newcommand{\OpDistance}{\bm{D}}
\newcommand{\OpCumsum}{\mathbfcal{C}}
\newcommand{\OpInt}{\mathbfcal{I}}
\newcommand{\OpCamera}{\mathbfcal{P}}
\newcommand{\MaskSun}{\mathbfcal{M}}
\newcommand{\Laplacian}{\mathbfcal{L}}
\newcommand{\OpDiag}[1]{\mathbb{D}\left\{#1\right\}}
\newcommand{\DistSet}{\mathcal{C}}
\newcommand{\DistUnknown}{\vect{n}}
\newcommand{\DistEstimated}{\hat{\vect{n}}}
\newcommand{\CostFunc}[1]{E(#1)}

%
% For the title
%
\newcommand\authnote[1]{\textsuperscript{\normalfont#1}}
\newcommand\affilnote[1]{\textsuperscript{\normalfont#1}}
\providecommand\textsuperscript[1]{$^{#1}$}

@@

Any voxel generally contains both air molecules and aerosols.  We
focus on situations where there is only a single type of aerosol over
a scene. Hence, the three-element vector $[{\sigma}^{\rm
  aerosol},\varpi^{\rm aerosol},g]$ is uniform across the scene, but
the density distribution ${\DistUnknown}$ is variable. As a numerical
approximation, assume that within any voxel, the molecular parameters
$\{ \beta^{\rm air}(k),\alpha^{\rm air}(k)\}$ and the aerosol density
$n(k)$ are constants, e.g., corresponding to the value at each voxel
center.  Following \cref{eq:tau}, the optical depth between the TOA
and voxel $k$ is
\begin{equation}
  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
  \label{eq:lSRn}
\end{equation}
We can write \cref{eq:lSRn} using matrix notation, $\vect{\tau}_{\rm
  SR}=\OpDistance^{\mathrm{Sun \rightarrow voxel}} \vect{\beta}$,
where $\vect{\tau}_{\rm SR}$ and $\vect{\beta}$ are column stack
vector representations of $\tau_{\rm SR}(k)$ and $\beta(q)$,
respectively. Similarly, the optical depth along a LOS to voxel $k$ is
expressed by element $k$ of $\vect{\tau}_{{\rm LOS}_c} =
\OpDistance^{\mathrm{voxel \rightarrow cam}} \vect{\beta}$ Here
$\vect{\tau}_{{\rm LOS}_c}$ is a column stack vector representation of
$\tau_{{\rm LOS}_c}(k)$.  The SR and LOS paths joining at each voxel
can form a single path from the TOA to camera $c$, yielding
\begin{equation}
  {\bm D}_c=
  {\bm D}^{\mathrm{Sun \rightarrow voxel}}+
  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
  \quad\text{ and }\quad
  \vect{\tau}_c=
  \vect{\tau}_{\rm SR}+
  \vect{\tau}_{{\rm LOS}_c}
  \;\;.
  \label{eq:D_tau_total}
\end{equation}

@@

In this paper, we assume that the type of the aerosol above an area is
known~\cite{Martonchik2009}. Hence, we focus on estimating the density
distribution $\DistUnknown$.
At hand, we have $N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
  measured}_c\}_{c=1}^{N_{\rm views}}$. The recovery task is phrased
as optimization of an objective function that fits the image-formation
model to the measured photographs, under constraints. Let $\DistSet$
be the set of all legitimate distributions, according to constraints.
Particularly, $\DistEstimated$ is non-negative, and it has limited spatial
support between the ground and the TOA. The optimization problem is,
\begin{equation}
  \label{eq:minobjectiveA}
  \DistEstimated =
  \argmin_{\DistUnknown \in \DistSet} \CostFunc{\DistUnknown}
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  \CostFunc{\DistUnknown}
  = \sum_{c=1}^{N_{\rm views}}
  \| \MaskSun \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2
  + \eta \Psi({\bm n})
\end{equation}
where $\MaskSun$ is a map that masks the areas around the sun, which are
overwhelmingly bright. %and the horizon.
% These regions are prone to dominant multiple scattering.
In Eq.~(\ref{eq:objectiveA}), $\Psi({\bm n})$ is a regularization term
that expresses some prior knowledge on the distribution, while $\eta$
is a regularization weight.  Since aerosol distributions are usually
fuzzy, it can be beneficial that regularization be a {\em smoothness
  term}, which penalizes energy in second order spatial derivatives
(3D Laplacian). Hence, we use
\begin{equation}
  \label{eq:regularizer}
  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2 = \| \Laplacian{\bm n}\|^2_2
\end{equation}
where $\Laplacian$ is a matrix representation of the 3D
\emph{Laplacian} operator.
